---
title: "Template HTML"
author: "Mariana"
date: "`r format(Sys.time(), '%d/%m, %Y')`"
output:
  bookdown::html_document2:
    fig_caption: true
    toc: false
bibliography: biblio.bib
csl: ecology.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F,comment = "#>")
library(tidyverse)
library(kableExtra)
library(DT)
library(plotly)
library(gapminder)
library(leaflet)
library(crosstalk)
```

# Example

This is a template rmd written in [@cran2022], with extended functionality thanks to the use of bookdown [@Xie_2016]. The use of references is not an enhancement, however the use of crossreferences to show figures and tables is only possible with this package.

As an example check figure \@ref(fig:mpg), and table \@ref(tab:mtcars).

```{r mpg, fig.cap= "This graph shows the relationship between the miles per galon of a car and their horsepower"}
data("mtcars")
ggplot(mtcars, aes(x = hp, y = mpg)) + geom_point() + geom_smooth(method = "lm") + theme_bw()
```


```{r mtcars}
kbl(mtcars, caption = "A nice table of mtcars") %>% 
  kable_paper() %>% 
  scroll_box(width = "800px", height = "500px")
```

## DT tables

```{r dt_table}
# Extensions to reorder columns and to add buttons
Test <- DT::datatable(Species_dataset, extensions = c('Buttons', 'ColReorder'),
          caption = 'Species abundances and explaining variables.',
          ## You can filter the data on top
            filter = "top",
          ## https://datatables.net/reference/option/dom
            options = list(dom = 'Blfrtip',
          ## you can reorder columns
                            colReorder = TRUE,
          ## You can scroll de table
                          scrollX='400px',
                           scrollY='200px',
          ## you can download or take away variables
                           buttons = c('copy', 'csv', 'excel', I('colvis')),
          ### how long you can make tables
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All"))))
                                             
# round the digits of these columns
Test %>%
    formatRound(columns = c("lon", "lat", "bio_1",
        "bio_2", "bio_3", "bio_4", "bio_5", "bio_6",
        "bio_7", "bio_8", "bio_9", "bio_10", "bio_11",
        "bio_12", "bio_13", "bio_14", "bio_15", "bio_16",
        "bio_17", "bio_18", "bio_19", "abund_sp1",
        "abund_sp2", "abund_sp4"), digits = 3)
```

## Interactive plots with `plotly`

```{r plotly}
Species2 <- Species_dataset %>%
    pivot_longer(cols = abund_sp1:abund_sp4, names_to = "Species",
        values_to = "Abundance") %>%
    mutate(Species = str_remove_all(Species, "abund_"),
        Species = str_replace_all(Species, "sp", "Spp "))

G <- ggplot(Species2, aes(x = bio_12, y = Abundance)) +
    geom_point(aes(color = Species)) + geom_smooth(aes(color = Species)) +
    theme_bw()

ggplotly(G)
```

```{r, animation}
df <- gapminder
fig <- df %>%
    plot_ly(x = ~gdpPercap, y = ~lifeExp, size = ~pop,
        color = ~continent, frame = ~year, text = ~country,
        hoverinfo = "text", type = "scatter", mode = "markers")

fig <- fig %>%
    layout(xaxis = list(type = "log"))

fig
```

```{r, leaflet}
leaflet(data = Species_dataset) %>%
    addTiles() %>%
    addCircles(lng = ~lon, lat = ~lat)
```


```{r, crosstalk}
sd <- SharedData$new(Species2)
crosstalk::filter_checkbox("Species", "Species", sd, ~Species)
crosstalk::filter_slider("Abundance", "Abundance", sd, ~Abundance, step = 10, round = T, min = min(Species2$Abundance), max = max(Species2$Abundance))

Numpal <- colorNumeric("viridis", sort(unique(Species2$Abundance)))


leaflet(sd) %>%
  addTiles() %>% 
  leaflet::addCircles(lng = ~lon, lat = ~lat, color = ~Numpal(Abundance), popup = ~paste("Abundance:", prettyNum(Abundance, big.mark = ",")), label = ~paste("Abundance:", prettyNum(Abundance, big.mark = ","))) %>%  addLegend("bottomright", pal = Numpal, values = ~Abundance,
    title = "Abundance",
    labFormat = labelFormat(big.mark =","),
    opacity = 1
  )

G <- ggplot(sd, aes(x = bio_12, y = Abundance)) + geom_point(aes(color = Species)) + theme_bw()

ggplotly(G)

DT::datatable(sd, extensions = c('Buttons', 'ColReorder'),
          caption = 'Species abundances and explaining variables.',
            filter = "top",
            options = list(dom = 'Blfrtip',
                            colReorder = TRUE,
                          scrollX='400px',
                           scrollY='200px',
                           buttons = c('copy', 'csv', 'excel', I('colvis')),
                           lengthMenu = list(c(10,25,50,-1),
                                             c(10,25,50,"All")))) %>%
    formatRound(columns=c("lon", "lat", "bio_1", "bio_2", "bio_3", "bio_4", "bio_5", 
"bio_6", "bio_7", "bio_8", "bio_9", "bio_10", "bio_11", "bio_12", 
"bio_13", "bio_14", "bio_15", "bio_16", "bio_17", "bio_18", "bio_19"), digits=3)
```



# References
