---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  warning = FALSE,
  error = FALSE,
  message = FALSE
)
```

# reproducibility

<!-- badges: start -->

<!-- badges: end -->

The goal of reproducibility is to make an example repository where I will work through examples of reproducible research. I will explore the Species_dataset and the relatioship between species abundances and climatic variables.

```{r packages}
library(tidyverse)
```

```{r read_data}
Species_dataset <- readr::read_csv2("Species_dataset.csv")
```

For example, in the following figure we will see the relationship between the abundances of species 4 and annual mean temperature

```{r plotspp4temp, fig.cap = "Temperature vs Abundance spp 4"}
ggplot(Species_dataset, aes(bio_1, abund_sp4)) +
  geom_point() +
  theme_bw()
```

Inline example: `r prettyNum(nrow(Species_dataset), big.mark = ",")`, the mean temperature in the sites is `r round(mean(Species_dataset$bio_1), digits = 1)`.

Try plotting a table:

```{r table}
head(Species_dataset[,1:4])
```

The file **first_html.Rmd** is a template of an html document with graphs, citations, crossreferences, etc.





